%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode
% Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/posquit0/Awesome-CV
%
% Author:
% Claud D. Park <posquit0.bj@gmail.com>
% http://www.posquit0.com
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Configuration
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Themes: Awesome-CV
\documentclass[]{awesome-cv}
\usepackage{textcomp}
%%% Override a directory location for fonts(default: 'fonts/')
\fontdir[fonts/]

%%% Configure a directory location for sections
\newcommand*{\sectiondir}{resume/}

%%% Override color
% Awesome Colors: awesome-emerald, awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis, awesome-concrete, awesome-darknight
%% Color for highlight
% Define your custom color if you don't like awesome colors
\colorlet{awesome}{awesome-black}
%\definecolor{awesome}{HTML}{CA63A8}
%% Colors for text
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

%%% Override a separator for social information in header(default: ' | ')
%\headersocialsep[\quad\textbar\quad]
    \begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Header
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}
	\headerfirstnamestyle{Drew J.} \headerlastnamestyle{ Mills} \\
	\vspace{2mm}
	{\faEnvelopeO\ \href{mailto:djmills@ucsd.edu}{djmills@ucsd.edu}} | {\faMobile\ +1 (858) 568-2968} | {\faGithub\ \href{https://github.com/pcsciencegeek}{pcsciencegeek }}|  {\faLinkedinSquare\ \href{https://linkedin.com/in/d1mills/}{ d1mills}} | {\faInternetExplorer \href{http://drewmills.co.uk/}{ DrewJMills.com}}
\end{center}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Education
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Education}
\begin{cventries}
	\cventry
	{B.S. in Cognitive Computer Science with Spec. in Machine Learning}
	{University of California, San Diego} 
	{}
	{June 2019}
	{}
\end{cventries}

\vspace{-5mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Experience
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Experience}
\begin{cventries}
	\cventry
	{Online Development Intern}
	{AMC Networks International}
	{London, UK}
	{June 2016 – July 2016}
	{\begin{cvitems}
		\item {Updated intranet to follow new guidelines}
		\item {Integrated intranet to Word Press}
		\item {Modified and updated CSS on business unit websites}
		\end{cvitems}}
	\cventry
	{Resident Assistant}
	{UC San Diego (Housing Dining Hospitality)}
	{San Diego, Ca}
	{July 2016 – Present}
	{\begin{cvitems}
		\item {Developed a positive living and learning environment designed to link community, faculty, and residents}
		\item {Promoted the interaction and construction of social networks}
		\item {Managed administrative duties including budgeting}
		\end{cvitems}}
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects & Coursework
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Projects \& Coursework}
\begin{cventries}
	\cventry
	{\begin{cvitems}
	    \item Via AWAKENS, ranked individuals by phenotype
        \item TODO
        \item TODO
    \end{cvitems}}
	{GenoMatch}
	{HTML, CSS, JavaScript}
	{}
	{}
	
	\vspace{-5mm}
	\cventry
	{\begin{cvitems}
        \item Designed a website for a Club
        \item Imported a template HTML5Up! template for the core design and interoperability between desktop and mobile environments
        \item Modified Bootstrap 4’s modal appearance to fit the specific aesthetic
    \end{cvitems}}
	{Anthropology Club Web page}
	{HTML, CSS, PHP, JavaScript}
	{}
	{}

	\vspace{-5mm}
	\cventry
	{\begin{cvitems}
        \item Program created pseudo bank account that allowed the user to deposit and spend money at different locations; each having different limitations. The program was written in C programming language. Implementing heavy use of functions, structures, arrays, pointers, logic, and standard libraries.
    \end{cvitems}}
	{Campus Cash Card (CSE 5A)}
	{C}
	{}
	{}

	\vspace{-5mm}
	\cventry
	{\begin{cvitems}
        \item Program is fully functioning replica of the game 2048. The game's objective is to slide numbered tiles on a grid and combine them to create a tile with the number 2048. Implementing heavy use of classes, objects, methods, constructors, arrays, references, logic and Java Class Libraries.
    \end{cvitems}}
	{2048 (CSE 8B)}
	{Java}
	{}
	{}

	\vspace{-5mm}
\end{cventries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Skills
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Skills}
\begin{cventries}
	\cventry
	{}
	{\def\arraystretch{1.15}{\begin{tabular}{ l l }
		Programming \& More:  & {\skill{ Java, C, HTML, CSS, JavaScript, \LaTeX, MySQL, Git, Unix Shell, Ubuntu}} \\
		\end{tabular}}}
	{}
	{}
	{}
\end{cventries}

\vspace{-7mm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Activities
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\cvsection{Activities}
\begin{cvhonors}
	\cvhonor
	{\begin{cvitems}
	    \item SD Hacks 2017
	\end{cvitems}}
	{}
	{}
	{}
\end{cvhonors}
\ 
\end{document}